A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-12 paper/ims-template.tex
New Tek formatting (aosgflp.tex. Use this from now on.

\begin{aug}
  \author{\fnms{Eric}  \snm{Mittman}\corref{}\ead[label=e1]{first@somewhere.com}},
  \author{\fnms{Colin} \snm{Lewis-Beck}\ead[label=e2]{second@somewhere.com}}
  \and
  \author{\fnms{William Q.}  \snm{Meeker}%
  \ead[label=e3]{third@somewhere.com}%
  \ead[label=u1,url]{http://www.foo.com}}

  %\thankstext{t2}{Footnote to the first author with the `thankstext' command.}

  %\runauthor{F. Author et al.}

  \affiliation{Iowa State University}

  \address{Address of the First and Second authors,\\ 
          \printead{e1,e2}}

  \address{Address of the Third author,\\
          \printead{e3,u1}}

\end{aug}

% indicate corresponding author with \corref{}
% \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% \thankstext{t1}{Thanks to somebody} 
% \address{line 1\\ line 2\\ printead{e1}}
%\author{\fnms{Eric Mittman and Colin Lewis-Beck and William Q. Meeker}}
%\affiliation{Iowa State University}
%\address{\printead{e1}}
%\and
%\author{\fnms{???} \snm{???}\ead[label=e2]{???}}
%\address{\printead{e2}}
%\affiliation{???}

>>>>

% indicate corresponding author with \corref{}
% \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% \thankstext{t1}{Thanks to somebody} 
% \address{line 1\\ line 2\\ printead{e1}}
\author{\fnms{Eric Mittman and Colin Lewis-Beck and William Q. Meeker}}
 \affiliation{Iowa State University}
%\address{\printead{e1}}
%\and
%\author{\fnms{???} \snm{???}\ead[label=e2]{???}}
%\address{\printead{e2}}
%\affiliation{???}
